Magnetic propeties of a two dimentional electron gas strongly coupled to lights

### 2021-04-10 theory/sec_02.tex
Add scattering potential model

@@

@@

@@

@@

    |U_{j'j}|^2 \sum_{l=-\infty}^{\infty} J_l^2\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]

@@

>>>>

\begin{equation} \label{2.23}

@@

\begin{equation} \label{2.24}

@@

\begin{equation} \label{2.25}

@@

\begin{equation} \label{2.26}

@@

    |U_{j'j}|^2

@@

\noindent
To avoid thee energy echange betwen a high-frequency field and electrons, the field should be purely dressing. We can achieve that by using the field with off-resonant and high frequency. Therefore, the only effect of the dressing field on 2DEG is the renormalization of the probability of elastic electron scattering within the same Landau level $(E_{n'}=E_n)$, which described by the term with $l=0$ the Eq. \eqref{2.26} leads to
\begin{equation} \label{2.27}
    \mathcal{W}_{j'j} = J_0^2\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
    \mathcal{W}_{j'j}^{(0)}
\end{equation}
where
\begin{equation} \label{2.28}
    \mathcal{W}_{j'j}^{(0)} = \frac{2\pi}{\hbar} |U_{j'j}|^2
    \delta(E_{n'} - E_{n})
\end{equation}
is the probability of scattering of a \textit{bare electron}. It is important to notice that the Bessel function factor depend on both the dressing field and stationaty magnetic field. This factor is responcible for all the effcts discussed in thisarticle.

\noindent
One can define the lifetime of the dressed electron at the Landau level $\tau$ is renormalized by the Bessel function as below
\begin{equation} \label{2.29}
    \frac{1}{\tau} \equiv \sum_{j'} \mathcal{W}_{j'j} =
    \sum_{j'}
    J_0^2\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
    \mathcal{W}_{j'j}^{(0)}
\end{equation}
where we have consider all posibilities that electron can jump to the state $j'$. Then rewrite the delat function as follows
\begin{equation} \label{2.30}
    \delta(\epsilon) =
    \frac{1}{\pi} \lim_{\Gamma \rightarrow 0 } \frac{\Gamma}{\Gamma^2 + \epsilon^2}
\end{equation}
where in this study we can assume that the paramater $\Gamma \equiv \hbar/\tau$ as scattering induced broading of the Landau level. But for the elestic scatteing within the same Landau level, we can write the $\delta$ function as
\begin{equation} \label{2.31}
    \delta(E_{n'} - E_{n}) \approx
    \frac{1}{\pi \Gamma}.
\end{equation}
Therefore Eq. \eqref{2.29} will change to
\begin{equation} \label{2.32}
    \frac{1}{\tau} =
    \sum_{j'}
    J_0^2\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
    \times
    \frac{2\pi}{\hbar} |U_{j'j}|^2 \times \frac{1}{\pi \Gamma}
\end{equation}
\begin{equation} \label{2.33}
    \frac{1}{\tau} =
    \sum_{j'}
    J_0^2\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
    \times
    \frac{2}{\hbar} |U_{j'j}|^2 \times \frac{\tau}{\hbar}
\end{equation}
and finally this can be modified to
\begin{equation} \label{2.34}
    \frac{1}{\tau} =
    \bigg[
    \frac{2}{\hbar^2}
    \sum_{j'}
    J_0^2\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
    |U_{j'j}|^2
    \bigg]^{1/2}
\end{equation}
where the summation is performed over electron states $j'$ within the same Landau level.

\noindent
Now lets specify more on the scattering potential where we can model them as randomly distributed delta fucntions as follows
\begin{equation} \label{2.35}
    U(\vb{r}) \equiv \sum_{i=1}^{N_s} U_0 \delta(\vb{r} - \vb{r}_i)
\end{equation}
where $N_s$ is the total number of scatters in the considering matel.
